---
title: "PeerAssignment1"
output: html_document
---

###Loading the data
```{r}
activity <- read.csv("activity.csv")
```

###What is mean total number of steps taken per day?
Calculate the total number of steps taken per day
```{r}
steps_per_day <- aggregate(activity$steps, by=list(date=activity$date), FUN=sum)
```

Histogram of the total number of steps taken each day
```{r,fig.width=510}
library(ggplot2)
ggplot(data=steps_per_day) + geom_histogram(aes(x=steps_per_day$date, y=steps_per_day$x), stat="identity") + labs(list(title = "Total number of steps", x = "date", y = "steps"))
```                                                                                                                

The mean and median of the total number of steps taken per day
```{r}
mean_steps <- mean(steps_per_day$x, na.rm = TRUE)
median_steps <- median(steps_per_day$x, na.rm = TRUE)
```
The mean = `r mean_steps`.
The median = `r median_steps`.

###What is the average daily activity pattern?
Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?